Fourmile Calibrations and Output

### 2024-09-24 fourmile_outputs_2013edits.Rmd
adding rd and rg hru outputs

>>>>

# HRU RD/RG

elev <- read_csv('./38HRU_sept2013_updates/hru_elev.csv')

rd1_grid <- hru_grids %>%
  dplyr::select(time, outRD1, ID) %>%
  mutate(source = 'grid') %>%
  left_join(., elev, by = 'ID') %>%
  arrange(time) %>%
  mutate(year = year(time)) %>%
  mutate(elevation_group = ntile(elevation, 4)) %>% 
  group_by(year, elevation_group) %>%
  mutate(rd1_summed = cumsum(outRD1))

rd1_statn <- hru_statn %>%
  dplyr::select(time, outRD1, ID) %>%
  mutate(source = 'statn') %>% 
  left_join(., elev, by = 'ID') %>%
  arrange(time) %>%
  mutate(year = year(time)) %>%
  mutate(elevation_group = ntile(elevation, 4)) %>% 
  group_by(year, elevation_group) %>%
  mutate(rd1_summed = cumsum(outRD1))

#rd1_hru <- bind_rows(rd1_grid, rd1_statn)

library(viridis)

rd1_grid_plot <- ggplot(rd1_grid, aes(x=time, y=rd1_summed, color=elevation_group)) + 
  geom_line() +
  scale_color_viridis_c() +  # Use a continuous viridis color palette
  theme_bw()

ggplotly(rd1_grid_plot)

rd1_statn_plot <- ggplot(rd1_statn, aes(x=time, y=rd1_summed, color=elevation_group)) + 
  geom_line() +
  scale_color_viridis_c() +
  theme_bw()

ggplotly(rd1_statn_plot)

###########################

rd2_grid <- hru_grids %>%
  dplyr::select(time, outRD2, ID) %>%
  mutate(source = 'grid') %>%
  left_join(., elev, by = 'ID') %>%
  arrange(time) %>%
  mutate(year = year(time)) %>%
  mutate(elevation_group = ntile(elevation, 4)) %>% 
  group_by(year, elevation_group) %>%
  mutate(rd2_summed = cumsum(outRD2))

rd2_statn <- hru_statn %>%
  dplyr::select(time, outRD2, ID) %>%
  mutate(source = 'statn') %>% 
  left_join(., elev, by = 'ID') %>%
  arrange(time) %>%
  mutate(year = year(time)) %>%
  mutate(elevation_group = ntile(elevation, 4)) %>% 
  group_by(year, elevation_group) %>%
  mutate(rd2_summed = cumsum(outRD2))

rd2_grid_plot <- ggplot(rd2_grid, aes(x=time, y=rd2_summed, color=elevation_group)) + 
  geom_line() +
  scale_color_viridis_c() +  # Use a continuous viridis color palette
  theme_bw()

ggplotly(rd2_grid_plot)

rd2_statn_plot <- ggplot(rd2_statn, aes(x=time, y=rd2_summed, color=elevation)) + 
  geom_line() +
  scale_color_viridis_c(option = 'mako') +
  theme_bw()

ggplotly(rd2_statn_plot)
